Outbreak Threshold Detection

### 2023-03-06 notebooks/Julia/simulation-detection.qmd
Add new jump simulation code with SDE problem Re-wrote the code for the Tau-leaping jump problem with births/deaths to try and work out some bugs. Chris Rackauckus suggested that it should use SDEProblem() rather than DiscreteProblem(), so had to add some functions to include Brownian/Wiener motion (as in a Jump-diffusion model).
Currently the jumps can go below 0, so need to use some kind of
switching to implement Direct Gillespie in these instances.

>>>>

```{julia}
function rate(out, u, p, t)
    out[1] = p[1] * u[1] * u[2] / (u[1] + u[2] + u[3] + u[4])         # β * S * I / N
    out[2] = p[2] * u[2]                        # σ * E
    out[3] = p[3] * u[3]                        # γ * I
    out[4] = p[4] * (u[1] + u[2] + u[3] + u[4])        # μ * N
    out[5] = p[4] * u[1]                        # μ * S
    out[6] = p[4] * u[2]                        # μ * E
    out[7] = p[4] * u[3]                        # μ * I
    out[8] = p[4] * u[4]                        # μ * R
    nothing
end

c = zeros(4, 8)
# S + I --> E
c[1, 1] = -1        # S -> S - 1
c[2, 1] = 1         # E -> E + 1

# E --> I
c[2, 2] = -1        # E -> E - 1
c[3, 2] = 1         # I -> I + 1

# I --> R
c[3, 3] = -1        # I -> I - 1
c[4, 3] = 1         # R -> R + 1

# S --> 2S
c[1, 4] = 1         # S -> S + 1

# S --> 0S
c[1, 5] = -1        # S -> S - 1

# E --> 0E
c[2, 6] = -1        # S -> S - 1

# I --> 0I
c[3, 7] = -1        # I -> I - 1

# R --> 0R
c[4, 8] = -1        # R -> R - 1

function change!(du, u, p, t, counts, mark)
    mul!(du, c, counts)
    nothing
end

rj = RegularJump(rate, change!, 8)

tmax = 2.0
δt = 0.1/365
tspan = (0.0, tmax)
tlength = length(tspan[1]:δt:tspan[2])
Random.seed!(1234);

u₀ = [999.0, 10.0, 0.0, 0.0]

μ = 1
β = 1000
σ = 365/8
γ = 365/5
p = (β, σ, γ, μ)

forcing!(du,u,p,t) = (du .= 0)
noise!(du,u,p,t) = (du .= 0)
W = WienerProcess(0.0,0.0,0.0)

prob = SDEProblem(forcing!, noise!, u₀, tspan, p, noise = W)
jump_prob = JumpProblem(prob, Direct(), rj)
sol = solve(jump_prob, EM(), dt = δt, maxiters = 1e5)
sol_array = zeros(5, length(sol))
sol_array[1:4, :] = Array(sol)
sol_array[5, :] = sum(sol_array[1:4, :], dims = 1)

fig = Figure()
ax = Axis(
    fig[1, 1],
    xlabel = "Time",
    ylabel = "Number"
)

lines!(ax, sol.t, sol_array[1, :], linewidth = 3, label = "S(t)")
lines!(ax, sol.t, sol_array[2, :], linewidth = 3, label = "E(t)")
lines!(ax, sol.t, sol_array[3, :], linewidth = 3, label = "I(t)")
lines!(ax, sol.t, sol_array[4, :], linewidth = 3, label = "R(t)")
lines!(ax, sol.t, sol_array[5, :], linewidth = 3, label = "N(t)")

fig

min(sol_array[1:5, :]...)
# min(sol_array[4, :]...)
```
